Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-15 draft.tex
move table captions above the tables and add vertical spaces
add bolding to the best results in the tables
some phrasing changes to decrease passive voice

	are typically out of the range of human hearing, and may not be directly reflect a vocal
	quality, otherwise referred to as "speaker-independent" features \cite{liu_hidden--wave_2023}.
	We use a new combination of features for our method, with an emphasis being placed on
	perceptible features, as we believe these to be the most likely to be understood by the
	layperson.

@@

			features that can be called generic, widely used in research involving the detection
			of synthetic while others are more specific and are cited accordingly. The features
			that are not summarized for a whole sample are extracted using a sliding window method,
			preventing a loss of fidelity that can be caused by compression of the feature to a
			standard size. The features we considered perceptible are as follows:

@@

			The first problem can be solved by taking the mean of the explanation weights of each

@@

@@

				3 hidden layers & standard & 10000 & 96.27\% & 0.03214 & 0.81763 \\

@@

				Simple & expand pitch\-flucs & 10000 & 93.31\% & 0.05661 & 0.92727 \\

@@

				MFCC & 0.7029 & 0.3753 \\

@@

				MFCC & 0.4383 & 0.2345 \\

@@

				MFCC & 0.2879 & 0.2408 \\

>>>>

	are typically out of the range of human hearing, and may not directly reflect a vocal quality,
	otherwise referred to as "speaker-independent" features \cite{liu_hidden--wave_2023}. We use a
	new combination of features for our method, with an emphasis being placed on perceptible
	features, as we believe these to be the most likely to be understood by the layperson.

@@

			features widely used in research involving the detection of synthetic while others are
			more specific and are cited accordingly. The features that are not summarized for a
			whole sample are extracted using a sliding window method, preventing a loss of
			fidelity that can be caused by compression of the feature to a standard size. The
			features we considered perceptible are as follows:

@@

			We solved the first problem by taking the mean of the explanation weights of each

@@

			\vspace{10pt}

@@

				3 hidden layers & standard & 10000 & \textbf{96.27\%} & \textbf{0.03214} & 0.81763 \\

@@

				Simple & expand pitch\-flucs & 10000 & 93.31\% & 0.05661 & \textbf{0.92727} \\

@@

				MFCC & \textbf{0.7029} & \textbf{0.3753} \\

@@

				MFCC & \textbf{0.4383} & \textbf{0.2345} \\

@@

				MFCC & \textbf{0.2879} & \textbf{0.2408} \\
